A Combinatorial Search of Parameterized Quantum Circuit Learning for Chemical Applications

### 2025-02-21 manuscript/main.tex
QCL

\subsection{BSE}
The first chemically relevant dataset we explore is the BSE49 dataset.
As highlighted in Figs. \ref{fig:bondtypes} and \ref{fig:BSEdistr}, this dataset consists of a diverse set of representative chemical bonds and bond separation energies.
Herein, we follow a similar analysis to the function fitting data, starting off with an analysis of a large set of PQCs using five and sixteen qubits with RUDs and ALs of 1.
From these two sets of data, we choose the best two models to study how an increase in the RUD and AL effects model performance.
[learning curves]
[Conclude we do not want to run this on real hardware due to the lack of promising results using simulation]

five qubit \ref{fig:5BSE_heatplots} \ref{fig:5BSE_boxplots}
best encoder-ansatz pair: train R$^{2}$/test R$^{2}$
Best encoder on average train R$^{2}$/test R$^{2}$
Best ansatz on average train R$^{2}$/test R$^{2}$

>>>>

\subsection{BSE}
To explore the performance of PQCs for chemically relevant datasets, the dataset we explore is the BSE49 dataset, which consists of a diverse set of bond separation energies and the related structures, as highlighted in Figs. \ref{fig:bondtypes} and \ref{fig:BSEdistr}.
Initially, we study the five qubit data, Figs. \ref{fig:5BSE_heatplots} and \ref{fig:5BSE_boxplots}, due to computational considerations.

five qubit 
best encoder-ansatz pair: train R$^{2}$/test R$^{2}$
Best encoder on average train R$^{2}$/test R$^{2}$
Best ansatz on average train R$^{2}$/test R$^{2}$
